---
title: Presenter Materials
execute: 
  echo: false
---

```{r}
#| include: false
library(tidyverse)
```

Below is the list of slides and posters from presenters with permission.


## Keynote


```{r}
name2title <- function(type) {
  readRDS(here::here("book/data/sessions.rds")) |> 
    filter(type == .env$type) |> 
    mutate(speakers = str_trim(speakers)) |> 
    select(speakers, titles) |> 
    deframe()
} 

name2time <- function(type) {
  days <- c(Monday = 1, Tuesday = 2, Wednesday = 3, Thursday = 4, Friday = 5)
  readRDS(here::here("book/data/sessions.rds")) |> 
    filter(type == .env$type) |> 
    mutate(speakers = str_trim(speakers),
           time = str_c(days[day], time, location)) |> 
    select(speakers, time) |> 
    deframe()
} 

list_slides <- function(type, folder = type, modify = c()) {
  fns <- fs::dir_ls(folder)
  bsn <- basename(fns)
  fns <- fns[str_detect(bsn, "^[^~]")]
  if(any(fs::is_dir(fns))) {
    fns[fs::is_dir(fns)] <- fs::dir_ls(fns[fs::is_dir(fns)], regexp = "[.]html$")
  }
  speakers <- str_extract(fns, ".+-(.+)[.](pdf|pptx|html)", group = 1)
  dict_title <- name2title(type)
  dict_time <- name2time(type)
  if(any(names(dict_title) %in% names(modify))) {
    ww <- which(names(dict_title) %in% names(modify))
    names(dict_title)[ww] <- modify[names(dict_title)[ww]]
    names(dict_time)[ww] <- modify[names(dict_time)[ww]]
  }
  tibble(file = paste0("/slides/", fns), 
         speaker = speakers, 
         title = unname(dict_title[speaker]),
         time = unname(dict_time[speaker])) |> 
  arrange(time) |> 
  #arrange(speaker) |> 
  select(file, speaker, title) |> 
  pwalk(function(file, speaker, title) {
    icon <- case_when(str_detect(file, "html$") ~ '<i class="fab fa-html5"></i>',
                      str_detect(file, "pdf$") ~ '<i class="fas fa-file-pdf"></i>',
                      str_detect(file, "pptx$") ~ '<i class="fas fa-file-powerpoint"></i>',
                      TRUE ~ '<i class="fas fa-link"></i>')
    cat(str_glue("- **{speaker}** \"{title}\" [{icon}]({file})\n\n"))
  })
}
```


```{r}
#| output: asis

list_slides("Keynote")
```

## Invited 

```{r}
#| output: asis
list_slides("Invited Session", "Invited")
```

## Contributed


```{r}
#| output: asis
list_slides("Talk", "Contributed", modify = c("A.A.P.N.M. Perera" = "Piumi Perera",
                                              "David I. Warton" = "David Warton",
                                              "Alec B. M. van Helsdingen" = "Alec van Helsdingen",
                                              "Alysha M. De Livera" = "Alysha De Livera",
                                              "Braden J. Thorne" = "Braden Thorne",
                                              "Colleen H Hunt" = "Colleen Hunt",
                                              "Christopher Bilder" = "Chris Bilder",
                                              "Michael H. Mumford" = "Michael Mumford",
                                              "Nelson J. Y. Chua" = "Nelson Chua",
                                              "Julian Taylor" = "Sam Rogers",
                                              "James M. Curran" = "James Curran",
                                              "Sandra K. Tanz" = "Sandra Tanz",
                                              "Scott D. Foster" = "Scott Foster",
                                              "Sharon  G. Nielsen" = "Sharon Nielsen",
                                              "Sean A. Martin" = "Sean Martin"))
```


## Posters

```{r}
#| output: asis
#| eval: false
# list_slides("Poster")
```

- **Sam Rogers** "Judgement Post-Stratification for Covariate Adjustment in Pairwise Comparisons in Block Designs" [<i class="fas fa-file-pdf"></i>](/slides/Poster/IBS2025RogersOzturkKravchuk-Sam Rogers.pdf)
- **Alice Richardson** "Visualisation of multinomial multilevel time-series modelling with application to current smoking status" [<i class="fas fa-file-pdf"></i>](/slides/Poster/Poster-Final-Final-Alice Richardson.pdf)
- **Damian Collins** "The “Theory of Sampling” (ToS) - have statisticians missed the boat?" [<i class="fas fa-file-pdf"></i>](/slides/Poster/posterTOS251121-Damian Collins.pdf) [<i class="fas fa-book"></i>](/slides/Poster/posterRefs.pdf)
